Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-06-03 analysis/preregistration_template.Rmd

*Describe how you will determine how reliable the data is for the given purpose. Ideally, model input data should be internally consistent across temporal and spatial scales and resolutions, and appropriate to the problem at hand [@Mahmoud2009].*

@@

*Data Exclusion: How will you determine what data, if any, will be excluded from your analyses? How will outliers be handled? Describe rules for identifying outlier data, and for excluding a site, transect, quadrat, year or season, species, trait, etc.*

*Missing data: How will you identify and deal with incomplete or missing data?*

>>>>

*Describe how you will determine how reliable the data is for the given purpose. Ideally, model input data should be internally consistent across temporal and spatial scales and resolutions, and appropriate to the problem at hand [@Mahmoud2009].* 
### 2.4.5 Data Evaluation: Data reliability reporting
### 2.4.5. Data Evaluation: data reliability reporting

@@

### 2.4.6. Data evaluation: data exclusion

*How will you determine what data, if any, will be excluded from your analyses? How will outliers be handled? Describe rules for identifying outlier data, and for excluding a site, transect, quadrat, year or season, species, trait, etc.*

### 2.4.7 Data Evaluation: Missing Data

*How will you identify and deal with incomplete or missing data?*
